<link rel="stylesheet" href="./css/flip.css" />
<link rel="stylesheet" href="./css/popup_style.css" />
<link rel="stylesheet" href="./css/style.css" />
<script type="text/javascript" src="./js/jquery-1.9.1.min.js"></script>
<script type="text/javascript" src="./js/nhpup-ioshack_1.0.js"></script>
<script type="text/javascript" src="./js/nhpup_1.0.js"></script>
<script type="text/javascript" src="./js/nhpup_1.1.js"></script>
<script type="text/javascript" src="./js/reports.js"></script>

```{r setup, include=FALSE}
# set global chunk options
lapply(c("knitr", "RWordPress", "xtable", "reports", "knitcitations",'ggplot2', 
	'XML', 'reshape2', "rCharts"), require, character.only = T)
opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, tidy = FALSE)

pressNum_n_dir <- "61803503/wp/"   #e.g., "61803503/wp/"
path2figureStorage <- "C:/Users/trinker/Dropbox/Public/wp/"   #e.g., "C:/Users/trinker/Dropbox/Public/wp/"
opts_knit$set(base.url = paste0("http://dl.dropboxusercontent.com/u/", pressNum_n_dir),
    base.dir = path2figureStorage)
bib <- read.bibtex(dir()[tools::file_ext(dir()) == "bib"][1])
```

`r IW("http://3.bp.blogspot.com/-ZoD0jyPPn2c/T5ASxK-hXLI/AAAAAAAACQQ/EArxD8xnUYw/s1600/olympic%2Bsymbol.jpg", width=140, height=70,side = "right")` For those who are addicted to R and haven't the time to click the mouse on a web browser you too can still be informed about the results of the [2014 Sochi Winter Olympics](http://www.sochi2014.com/).  I was inspired by [a SO response](http://stackoverflow.com/questions/11712353/downloading-live-olympic-medal-data-into-r) around the London games a couple years back.

## Packages to Load

```{r, eval=FALSE}
packs <- c("knitr", "ggplot2", "XML", "reshape2", "rCharts")
lapply(packs, require, character.only = T)
```	
	
# The Script

```{r}
olympics <- 
function(theurl = "http://www.sochi2014.com/en/medal-standings", include.zero = FALSE) {
 
    invisible(lapply(c('ggplot2', 'XML', 'reshape2') , require, character.only=TRUE))
 
    ## Grab Data, Clean and Reshape
    raw <- readHTMLTable(theurl, header=TRUE, 
        colClasses = c(rep("factor", 2), rep("numeric", 4)))
    raw <- as.data.frame(raw)[, -1]
    colnames(raw) <- c("Country",  "Gold", "Silver", "Bronze", "Total")
    raw <- with(raw, raw[order(Total, Gold, Silver, Bronze), ])
    if (!include.zero) {
        raw <- raw[raw[, "Total"] != 0, ]
    }
    raw[, "Country"] <- factor(raw[, "Country"], levels = raw[, "Country"])
    rownames(raw) <- NULL
    mdat <- melt(raw, value.name = "Count", variable.name = "Place", id.var = "Country")
    mdat[, "Place"] <- factor(mdat[, "Place"], 
        levels = c("Bronze", "Silver", "Gold", "Total")) 
 
    ## Plot the Data
    plot1 <- ggplot(mdat, aes(x = Count, y = Country, colour = Place)) +
      geom_point() +
      facet_grid(.~Place) + theme_bw()+
      scale_colour_manual(values=c("#CC6600", "#999999", "#FFCC33", "#000000")) 
    print(plot1)
 
    return(invisible(raw))
}
```


# The Visual Results

```{r, fig.width=12, fig.height=4.5}
x <- olympics()
```

# As a Data Table

```{r, results = 'asis', comment = NA}
dTable(x)$show('inline', include_assets = TRUE, cdn = TRUE)
```
<br>

WordPress and Data Table don't play well together so you'll need to run the code to see it in action.

# Discussion

I have chosen a dot plot to display the data because it's easy to quickly get a sense of the data yet be able to compare relatively easily.  Dot plots take advantage of the powerful pre-attentive attribute of distance (The most powerful way to visually convey quantitative information).  Stephen Few gives his two cents about dot plots [here](http://www.perceptualedge.com/articles/b-eye/dot_plots.pdf).

I'm lazy but this would be a fun [Shiny app](http://www.rstudio.com/shiny/) to build.

Thanks to @Ramnath for [help implementing](https://github.com/yihui/knitr/issues/717#issuecomment-34590101) the chart as a [jQuery DataTable](http://www.datatables.net/).


<hr><em><font size="1">*Created using the `r HR2("https://github.com/trinker/reports", "reports")` package</font></em>
